Convex Surrogates via Polyhedral Losses

### 2019-04-02 jessie-writeup/jessie-notes.tex
Reorganizing

	\item For abstain, we might want an extra, redundant normal $(0,0) \in V$ so that the vectors of $V$ are the embedded reports?  
	(Requires getting rid of assumption that normals are in general position.)

	\item Do we want to test this construction for ranking on 3 outcomes?  (See below)

@@

The polytopes then appear as follows (and are similar for each cell.)
The large triangle that the polytopes are all inside is $V^\circ$.
\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{./ranking}
\caption{Polytopes $T(*, y)$ for each $y \in \Y$.}
\label{fig:ranking}
\end{figure}

>>>>

@@

The polytopes then appear as in Figure~\ref{fig:ranking-polytopes} (and are similar for each cell.)
The large triangle that the polytopes are all inside is $V^\circ$.
\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{./ranking}
\caption{Polytopes $T(*, y)$ for each $y \in \Y$.}
\label{fig:ranking-polytopes}
\end{figure}

I still haven't reverse engineered this to construct a loss, but that's a task for another day.
It would be interesting to compare such a loss to the one we constructed all that time ago.

	\item For abstain, we might want an extra, redundant normal $(0,0) \in V$ so that the vectors of $V$ are the embedded reports?  
	(Requires getting rid of assumption that normals are in general position.)
	After working through ranking, I have a hunch this doens't always work, though.

	\item Would be interesting to look at ranking loss.
